---
output: github_document
bibliography: ./vignettes/literature.bib
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


[![License: GPL v3](https://img.shields.io/badge/License-GPLv3-blue.svg)](https://www.gnu.org/licenses/gpl-3.0)
[![Travis-CI Build Status](https://api.travis-ci.org/PolMine/europarl.svg?branch=master)](https://travis-ci.org/PolMine/europarl)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/PolMine/europarl?branch=master&svg=true)](https://ci.appveyor.com/project/PolMine/europarl)


## About the 'europarl' R package

This is a R data package that includes minimal functionality to download a
subset of the Europarl Corpus [@koehn2005epc], version 3, pre-indexed for the IMS Open Corpus
Workbench [@EvertHardie2011]. It is based on the POS-tagged, lemmatised and sentence-aligned
distribution offered by the [OPUS project](http://urd.let.rug.nl/tiedeman/OPUS/Europarl3.php) 
and covers the languages
English, Dutch, French, German, Italian and Spanish. The six corpora are
available under the CWB names EUROPARL-EN, EUROPARL-NL, EUROPARL-FR,
EUROPARL-DE, EUROPARL-IT and EUROPARL-ES.


## Installation

The easiest way to install the *europarl* package is to install it from the
[drat](https://cran.r-project.org/web/packages/drat/vignettes/DratFAQ.html)-repository
of the [PolMine Project](http://www.polmine.de).

```{r, eval = FALSE}
install.packages("europarl", repos = "https://polmine.github.io/drat")
```

The package  includes only a simple installer function `europarl_download()`
that will download the Europarl corpus from the default location (a server of the
University of Erlangen).

```{r download_corpus, eval = FALSE}
europarl::europarl_download()
```

Note that the tarball that is downloaded is larger than 2GB. A good internet
connection and some patience will be an advantage. 

The indexed corpus will be stored in a subdirectory of the package (./extdata/cwb/).


## Usage

The idea to use R packages for shipping corpora has been developed in the context
of the PolMine Project [@blaette2018]. The most convenient way to use the data
will be to use the [polmineR](https://CRAN.R-project.org/package=polmineR) package.
To be able to access that data within the package, call the `use()`-function.

```{r, eval = FALSE}
if (!"polmineR" %in% rownames(installed.packages())) install.packages("polmineR")
library(polmineR)
use("europarl")
```

If the corpora have been downloaded, you should see something like this.

```{r use_europarl,echo = FALSE}
library(polmineR)
use("europarl")
```

The polmineR package offers a basic vocabulary for corpus analysis (counting,
keyword-in-context analysis, cooccurrences, keyword extraction etc.). To learn
more about the polmineR package, consult the [package documentation](http://polmine.github.io/polmineR/). To get started, you might
want to perform a simple counting operation, such as counting the number of
occurrences of "European integration" using the syntax of the Corpus Query
Processor (CQP).

```{r}
count("EUROPARL-EN", query = '"European" "Integration" %c', cqp = TRUE)
```

## Achknowledgements and Citation

The effort necessary to write this package has been fairly limited. The original work
has been done by Philipp Koehn (University of Edinburgh), see the [website of the OPUS project](http://opus.nlpl.eu/Europarl3.php), and the [Wikipedia entry on the Europarl Corpus](https://en.wikipedia.org/wiki/Europarl_Corpus).

Following the advice on the [website of the OPUS project](http://opus.nlpl.eu/Europarl3.php),
the paper "Parallel Data, Tools and Interfaces in OPUS" [@tiedemann2012] should be quoted 
as a reference to the Europarl corpus.

Last but not least, Stefan Evert's efforts to prepare and host the linguistically annotated
version of Europarl as a CWB indexed corpus is gratefully acknowledged.


## References

